Ecological network control

### 2018-06-18 paper/supp-info.Rmd
Fixed effects model selection table for species level

tab_cc %>%
  dplyr::bind_rows(tab_su) %>%
  dplyr::mutate(random = pretty_term_names(random)) %>%
  dplyr::rename(`random effects` = random) %>%
  knitr::kable("latex", 
               booktabs = T, 
               caption = "Selection table of the random effects in the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$. Only models with a weight larger than 0.01 are shown. We modelled the probability of being a superior node without random effects as the random intercept over site had zero variance.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
  kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
```
```

>>>>

tab_cc %>%
  dplyr::bind_rows(tab_su) %>%
  dplyr::mutate(random = pretty_term_names(random)) %>%
  dplyr::rename(`random effects` = random) %>%
  knitr::kable("latex", 
               booktabs = T, 
               caption = "Selection table of the random effects in the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$. Only models with a weight larger than 0.01 are shown. We modelled the probability of being a superior node without random effects as the random intercept over site had zero variance.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
  kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
```

```{r tab-model-output-species-level}
best_model_cc <- species_model_cc %$%
  fixed %>%
  get_best_model() 
best_model_su <- species_model_superior %$%
  fixed %>%
  get_best_model()

num_effects <- get_num_effects(best_model_cc)

table_df <- best_model_cc %>%
  broom::tidy() %>%
  dplyr::bind_rows(broom::tidy(best_model_su))

table_df %>%
  dplyr::mutate(group = dplyr::if_else(is.na(group), "fixed", group)) %>%
  dplyr::select(group, term, estimate, std.error, statistic, p.value) %>%
  dplyr::mutate(term = pretty_term_names(term)) %>%
  knitr::kable("latex", 
               col.names = c("effect type", "term", "estimate", "std. error", "z value", "p value"),
               booktabs = T, 
               caption = "Summary table of the control capacity model with the smallest AICc.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("control capacity models", 1, purrr::reduce(num_effects, sum)) %>%
  kableExtra::group_rows("superior probability models", purrr::reduce(num_effects, sum) + 1, nrow(table_df))

```
```
